---
title: "GLOBIOM-G4M-link"
subtitle: R notebook for automatizing the link between GLOBIOM and G4M.
author:
- Andrey L. D. Augustynczik
- Albert Brouwer 
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_notebook
---

For an introduction and requirements, [read the README](https://github.com/iiasa/GLOBIOM-G4M-link/blob/main/README.md). Run the code chunks in first-to-last order. You can have RStudio run all chunks in one go, but to configure and test your setup---and because some chunks take a long time to run---it is advisable to start out by running chunks one-by-one at least until you have verified that everything is working smoothly.

Carefully check the output of each chunk for errors, and if present make adjustments and re-run the chunk that failed.

The repository includes a default configuration file `R/default_configuration.R`. To adjust the configuration to your requirements, copy the default configuration file to a new file at `R/configuration.R` and edit that copy. Your
adapted copy will be checked against the defaults.

## Process the configuration

```{r}
# Remove any objects from active environment and read the default configuration
rm(list=ls())
source("R/configuration/default.R")

# Collect the names and types of the default config parameters
config_names <- ls()
if (length(config_names) == 0) {stop("Default configuration is absent! Please restore the default configuration. It is required for configuration checking, also when providing a separate configuration file.")}
config_types <- lapply(lapply(config_names, get), typeof)
# Can now add to the active environment
source("R/configuration/optional.R")

# Point to the customized configuration file
configuration_file <- "R/configuration/custom.R"

# Load packages
library(gdxrrw)
library(gdxtools)
suppressWarnings(library(tidyverse))
library(stringr)

# Remove mandatory config defaults from the global scope
rm(list=config_names[!(config_names %in% OPTIONAL_CONFIG_SETTINGS)])

# Source the config file, should add mandatory config settings to the global scope
source(configuration_file, local=TRUE, echo=FALSE)

# Check that all config settings exist, this catches mandatory settings missing in the config file
for (i in seq_along(config_names))  {
  name <- config_names[i]
  if (!exists(name)) stop(str_glue("Mandatory config setting {name} is not set in config file {args[1]}!"))
  type <- typeof(get(name))
  if (type != config_types[[i]] &&
      name != "RESOLUTION_DOWNSCALING" && # R has no stable numerical type
      type != "NULL" && # allow for configured vector being empty
      config_types[[i]] != "NULL" # allow for default vector being empty
  ) stop(str_glue("{name} set to wrong type in {configuration_file}, type should be {config_types[[i]]}"))
}
rm(config_names, config_types)
```

## Set up directories and functions

```{r}

# Cache working directory
cd <- getwd()

# Determine temporary directory for this R session
td <- tempdir()
fsep <- ifelse(str_detect(td, fixed("\\") ), "\\", ".Platform$file.sep") # Get the platform file separator: .Platform$file.sep is set to / on Windows
TEMP_DIR <- str_replace_all(td, fixed(fsep), .Platform$file.sep)
rm(td, fsep)

# Source support functions
source("R/globiom_g4m_functions.R")
source("R/helper_functions.R")
```

## Perform the initial GLOBIOM run

```{r}
# Run GLOBIOM
run_globiom_initial(cd)

print("Initial GLOBIOM run complete.")
```

## Perform the initial downscaling - needs data from the initial GLOBIOM run

```{r}
if (!file.exists(str_glue(WD_DOWNSCALING,"/input/","output_landcover_",PROJECT,"_",DATE_LABEL,".gdx"))) stop("File for downscaling not found! Please call the intial GLOBIOM run before downscaling")

run_downscaling(cd)

print("Initial downscaling complete")
```

## TODO: Run G4M - needs data from the intial downscaling

```{r}
if (!file.exists(str_glue(PATH_FOR_G4M,"/",GDX_OUTPUT_NAME,"_output_",PROJECT,"_",DATE_LABEL))) stop("File for G4M run not found! Please call the intial downscaling before the G4M run")
    
# Run G4M
```

## TODO: Perform the final GLOBIOM run - needs data from the G4M run

```{r}
# Run GLOBIOM
```

## TODO: Perform the final downscaling - needs data from the final GLOBIOM run


```{r}
# Run final downscaling
```
